\bf On semidefinite representable sets over valuation fields

### 2024-11-19 article/paper_padic_spec.tex
section 4

\begin{proposition}
  {\color{blue} [Peut être une hypothèse à rajouter, par exemple $K$ à valuation discrete]}
  The set $K^{d \times d}_+$ is both open and closed.
\end{proposition}
\begin{proof}
Firstly, $\OK[X]$ is closed and open in $K[X]$ equipped with the infinitiy norm $\|\cdot\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|$. $\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ that induces a discrete distance for which open balls are also closed sets.
Furthermore, $K^{d\times d}_+ = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps a matrix to its characteristic polynomial which is continuous.
\end{proof}

@@

\begin{remark}
  \corentin{Pas nécessairement très important, à voir}
  If $C$ is a cone that is furthermore closed under addition (what shall be called a convex cone in the real case) then $C$ is a $\OK$-module.
\end{remark}

\begin{proposition}
  The set $K^{d \times d}_+$ is a cone.
\end{proposition}
\begin{proof}
  The result is immediate following the definiton of $K^{d \times d}_+$.
\end{proof}

@@

\begin{remark}
  As in the real case, one often abuses of notation, saying that the preimage
  $S_A = \varphi_A^{-1}(K^{d \times d}_+) = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}$
  of $K^{d \times d}_+$ under the map $\varphi_A : K^n \to \mathcal{L} \subset K^{d \times d}$, defined as
  $\varphi_A(x) = A_0+x_1A_1+\cdots+x_nA_n$, is a \emph{spectrahedron
  in $K^n$}. Remark that the map $\varphi_A$ is in general not injective, unless $A_1,\ldots,A_n$ are linearly
  indepedent.
\end{remark}

\begin{remark}
  The class of spectrahedra in $K^{d \times d}$ (or in $K^n$) is closed under intersection: indeed one
  has $(\mathcal{L}_1 \cap K^{d \times d}_+) \cap (\mathcal{L}_2 \cap K^{d \times d}_+) =
  (\mathcal{L}_1 \cap \mathcal{L}_2) \cap K^{d \times d}_+$ and
  $S_A \cap S_B = S_{\diag(A,B)}$, for two affine spaces $\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$
  et $\mathcal{L}_2 = A_0+\span{B_1,\ldots,B_n}$.
\end{remark}

@@

\begin{proposition}
  Spectrahedra are semialgebraic sets. 
\end{proposition}

\begin{proof}
  Let $S$ be spectrahedron and $A$ a linear matrix such that $S={x \in K^n : A(x) \succeq 0}$. 
  We denote as $p_i(x)$ the $i$-th coefficient of $\chi_{M(x)}$. The map $p_i	: x \to p_i(x)$ is polynomial and $x \in S$ if and only if $\val(p_i(x)) \geq 0$ for $i=0,...,d$.

  Finally, by \ref{caracsdp}, $S = \{x \in K^n : \chi_{M(x)} \in \OK(T)\} = \bigcap\limits_{i=0}^d \{x \in K^n : \val(p_i(x)) \geq 0\}$.
\end{proof}

\corentin{ Une autre définition qu'il pourrait être intéressant d'explorer. Attention! Pas les mêmes propriétés.}
\begin{definition}[Alternative definition]
  Let $A_0, ..., A_n, B_0, ..., B_n \in M_{d,d}(K)$. 
  We denote as $S^+_A$ the set $S_{A}^+ = \left\{ x \in K^n : A_0 + x_1 A_1+ ...+x_nA_n \succeq 0  \right\}$ and $S^-_B$ denotes the set $S^-_B = \left\{ x \in K^n : B_0 + x_1 B_1+ ...+x_nB_n \preceq 0\right\}$. 
  The set $S_A,B := S_A^+ \cup S_B^-$ is called a \emph{spectrahedron}.
\end{definition}

>>>>

@@

\begin{proposition}
%  {\color{blue} [Peut être une hypothèse à rajouter, par exemple $K$ à valuation discrete]}
  $K^{d \times d}_+$ is a cone.
  If $\val$ is discrete, then it is both open and closed.
\end{proposition}
\begin{proof}
  The fact that $K^{d \times d}_+$ is a cone is immediate from the definition.
  Next, remark that $\OK[X]$ is closed and open in $K[X]$ equipped with the infinity norm
  $$
  \|\cdot\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to
  \max_{1 \leq k \leq n} |a_k|,
  $$
  {where $|\cdot|$ is any norm induced by $\val$}:
  $\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ that induces a discrete distance for
  which open balls are also closed sets.
  Furthermore, $K^{d\times d}_+ = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps a
  matrix to its characteristic polynomial which is continuous.
  Thus $K^{d\times d}_+$ is both open and closed, too.
\end{proof}

%\begin{remark}
%  \corentin{Pas nécessairement très important, à voir}
%  If $C$ is a cone that is furthermore closed under addition (what shall be called a convex cone in the real case) then $C$ is a $\OK$-module.
%\end{remark}

@@

\begin{remark}
  As in the real case, one often abuses of notation, saying that the preimage
  $S_A = \varphi_A^{-1}(K^{d \times d}_+) = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}$
  of $K^{d \times d}_+$ under the map $\varphi_A : K^n \to \mathcal{L} \subset K^{d \times d}$, defined as
  $\varphi_A(x) = A_0+x_1A_1+\cdots+x_nA_n$, is a \emph{spectrahedron
  in $K^n$}. Remark that the map $\varphi_A$ is onto $\mathcal{L}$ but not injective,
  unless $A_1,\ldots,A_n$ are linearly indepedent.
\end{remark}

The class of spectrahedra in $K^{d \times d}$ (or in $K^n$) is closed under intersection: indeed one
has $(\mathcal{L}_1 \cap K^{d \times d}_+) \cap (\mathcal{L}_2 \cap K^{d \times d}_+) =
(\mathcal{L}_1 \cap \mathcal{L}_2) \cap K^{d \times d}_+$ and
$S_A \cap S_B = S_{\diag(A,B)}$, for two affine spaces $\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$
et $\mathcal{L}_2 = A_0+\span{B_1,\ldots,B_n}$.
Moreover this class contains polyhedra in $K^n$.

@@

\begin{proposition}
  Spectrahedra in $K^n$ are semialgebraic sets. 
\end{proposition}

\begin{proof}
  Let $S = S_A \subset K^n$ be spectrahedron, for some linear matrix $A(x) = A_0+\sum_{i=1}^n x_i A_i$. 
  Denote by $p_i(x) \in K[x]$ the $i$-th coefficient of $\chi_{A(x)}$, $i=0,\ldots,d$.
  By \Cref{caracsdp} one has:
  $$
  S = \left\{x \in K^n : \chi_{A(x)} \in \OK[T]\right\}
  = \bigcap_{i=0}^d \{x \in K^n : \val(p_i(x)) \geq 0\}.
  $$
\end{proof}

%\corentin{ Une autre définition qu'il pourrait être intéressant d'explorer. Attention! Pas les mêmes propriétés.}
%\begin{definition}[Alternative definition]
%  Let $A_0, ..., A_n, B_0, ..., B_n \in M_{d,d}(K)$.  We denote as $S^+_A$ the set $S_{A}^+ = \left\{ x \in K^n : A_0 + x_1 A_1+ ...+x_nA_n \succeq 0  \right\}$ and $S^-_B$ denotes the set $S^-_B = \left\{ x \in K^n : B_0 + x_1 B_1+ ...+x_nB_n \preceq 0\right\}$.   The set $S_A,B := S_A^+ \cup S_B^-$ is called a \emph{spectrahedron}.
%\end{definition}
